---
title: "Rfinal"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rfinal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## This package is used for data analyis. It can be used in a dataframe.
- It has functions for four different usages:
  + Read dataset
  + Summarize dataset
  + Statistical functions(correlation and simple linear regression)
  + Visualization (histograms)


## There will be examples showing how to use the functions in this package.

```{r setup}
library(Rfinal)
```

## Example 1: get a histogram of a continous variable

```{r}
get_histogram_final(cars, "speed")
```

## Example 2: get data summaries
```{r}
get_summarize_final(cars, "speed")
```
It will return the mean, standard deviation, median, maximum and minimum of the variable.


## Example 3: get a simple linear regression model between two variables
```{r}
get_lm_final(cars, "speed", "dist")
```
It returns the parameter estimates and other statistics of the model. The simple 
linear regression model between speed and dist is:
$$
speed = 8.28391 + 0.16557 * dist
$$
